---
title: "Centraldogmagroup19"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Centraldogmagroup19}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r}
install.packages("Centraldogmagroup19")
```


```{r setup}
library(Centraldogmagroup19)
```

This package can be used to create plot showing the frequency of amino acids based on a DNA sequence input. It consists of 5 functions: Function1 generates a random DNA sequence, where the length is defined by the user. Function2 converts the DNA sequence into RNA. Function3 divides the sequence into individual codons given the readin frame, which is defined by the user. Function 4 translates the codons into amino acids. Function 5 plots the frequency of each amino acid in the sequence in a nice bar plot. 

## Function1

The first function of the package takes as input a number, which defines the length of a randomly generated DNA sequence. In the example below, 20 is used as input, and the function then generates a DNA sequence consisting of 20 random bases.

```{r}
Centraldogmagroup19::function1(20)
```


## Function3

The third function of the package takes a DNA or RNA sequence and divides it into strings of 3 (aka codons). Moreover, you can define the reading frame in the input of the function. The output is codons with three bases in each. Example:

```{r}
Centraldogmagroup19::function3("AUGAAAGUAGGUCC")
```


## Function4

The fourth function of the package takes as input a list of strings representing codons generated by function3. It then uses the table shown below (codon_table) to translate each codon into amino acids, as illustrated in the example below.

```{r}
codon_table <- c("UUU" = "F", "UCU" = "S", "UAU" = "Y", "UGU" = "C",
                 "UUC" = "F", "UCC" = "S", "UAC" = "Y", "UGC" = "C",
                 "UUA" = "L", "UCA" = "S", "UAA" = "_", "UGA" = "_",
                 "UUG" = "L", "UCG" = "S", "UAG" = "_", "UGG" = "W",
                 "CUU" = "L", "CCU" = "P", "CAU" = "H", "CGU" = "R",
                 "CUC" = "L", "CCC" = "P", "CAC" = "H", "CGC" = "R",
                 "CUA" = "L", "CCA" = "P", "CAA" = "Q", "CGA" = "R",
                 "CUG" = "L", "CCG" = "P", "CAG" = "Q", "CGG" = "R",
                 "AUU" = "I", "ACU" = "T", "AAU" = "N", "AGU" = "S",
                 "AUC" = "I", "ACC" = "T", "AAC" = "N", "AGC" = "S",
                 "AUA" = "I", "ACA" = "T", "AAA" = "K", "AGA" = "R",
                 "AUG" = "M", "ACG" = "T", "AAG" = "K", "AGG" = "R",
                 "GUU" = "V", "GCU" = "A", "GAU" = "D", "GGU" = "G",
                 "GUC" = "V", "GCC" = "A", "GAC" = "D", "GGC" = "G",
                 "GUA" = "V", "GCA" = "A", "GAA" = "E", "GGA" = "G",
                 "GUG" = "V", "GCG" = "A", "GAG" = "E", "GGG" = "G")
```

```{r}
Centraldogmagroup19::function4("CUC","AAU","CGC","GAU","AAA")
```

